%-------------------------
% Resume in Latex
% Author : Jake Gutierrez
% Based off of: https://github.com/sb2nov/resume
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}

\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item \small{
    {#1}
  }\vspace{-4pt} % Adjust this to match the spacing of other sections
}


\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\newenvironment{tightItemize}{%
  \begin{itemize}[leftmargin=0.15in]
  \setlength{\itemsep}{0pt}%
  \setlength{\parskip}{0pt}%
}{%
  \end{itemize}
}



\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}

%----------HEADING----------
\begin{center}
    \textbf{\Huge \scshape Alissa Baza} \\ \vspace{1pt}
    \small (559)869-7791 $|$ \href{mailto:alissabaza@gmail.com}{\underline{alissabaza@gmail.com}} $|$ 
    \href{https://linkedin.com/in/alissa-baza}{\underline{linkedin.com/in/alissa-baza}} \\
\end{center}

%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {University of California, Los Angeles (UCLA)}{Los Angeles, CA}
      {Bachelor of Arts in Psychology, Minor in Education}{Sept. 2022 -- June 2024}
  \resumeSubHeadingListEnd

%-----------EXPERIENCE-----------
\section{Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {Behavior Intervention Aid}{Aug. 2024 -- Present}
      {Kennedy Elementary School}{Dinuba, CA}
      \resumeItemListStart
        \resumeItem{Organize group meetings to foster a sense of community among mentees while setting expectations for communication and support.}
        \resumeItem{Applied behavior modification techniques based on Applied Behavior Analysis (ABA) principles to improve students’ social interaction skills.}
        \resumeItem{Responded appropriately to disruptive, abusive, and dangerous behavior by following established procedures.}
      \resumeItemListEnd

    \resumeSubheading
      {MEChA Calmecac Academic Peer Counselor}{Oct. 2023 -- June 2024}
      {University of California, Los Angeles}{Los Angeles, CA}
      \resumeItemListStart
        \resumeItem{Provided weekly one-on-one counseling to students, aiding academic progress, planning, and holistic wellbeing.}
        \resumeItem{Managed counseling services, evaluated service effectiveness, and tracked counseling services using Excel.}
        \resumeItem{Conducted outreach including phone banking, email communication, and tabling to promote MEChA Calmecac.}
        \resumeItem{Assisted in facilitating academic and holistic workshops each quarter, enhancing student engagement and learning.}
      \resumeItemListEnd

    \resumeSubheading
      {Summer Recreation and Enrichment Aid}{June--July 2022, June--July 2023}
      {Cutler Elementary School}{Cutler, CA}
      \resumeItemListStart
        \resumeItem{Delivered instruction in subjects like math, science, reading, and grammar.}
        \resumeItem{Assisted in classroom and playground setup, ensuring a safe and healthy environment.}
        \resumeItem{Maintained discipline and fostered a positive atmosphere through leadership and responsibility.}
      \resumeItemListEnd

    \resumeSubheading
      {A.V.I.D. Tutor}{Jan. 2021 -- June 2022}
      {Orosi High School}{Orosi, CA}
      \resumeItemListStart
        \resumeItem{Recommended and recruited other AVID team members and coordinated AVID fundraising activity.}
        \resumeItem{Tutored students across various subjects, reinforcing class lessons and improving their skills and test preparation.}
        \resumeItem{Collaborated with teachers to assess and address the educational needs of students based on observed performance.}
        \resumeItem{Corrected assignments, including class and homework tasks in writing, spelling, punctuation, and arithmetic.}
        \resumeItem{Operated various classroom and office equipment, including computers and audio-visual tools.}
      \resumeItemListEnd

  \resumeSubHeadingListEnd

%-----------RESEARCH-----------
\section{Research}
\resumeSubHeadingListStart
    \resumeSubheading
      {Latinx Mental Health and Retention in Higher Education}{Sept. 2023 -- Dec. 2023}
      {University of California, Los Angeles}{Los Angeles, CA}
      \resumeItemListStart
        \resumeItem{Analyzed interviews from MEChA Calmecac to assess support structures for underserved students.}
        \resumeItem{Identified barriers, such as limited resources and cultural dissonance, affecting students’ academic success and well-being.}
        \resumeItem{Proposed recommendations to improve culturally relevant mental health resources and peer counseling programs for Latinx students.}
      \resumeItemListEnd
\resumeSubHeadingListEnd

%-----------VOLUNTEER-----------
\section{Volunteer}
\resumeSubHeadingListStart
    \resumeSubheading
      {Transfer Mentor}{Sept. 2023 -- June 2024}
      {University of California, Los Angeles}{Los Angeles, CA}
      \resumeItemListStart
        \resumeItem{Maintained regular contact with mentees via emails, calls, and texts to assess and address their concerns.}
        \resumeItem{Established ground rules for interactions, ensuring respect for personal schedules and communication methods.}
        \resumeItem{Organized meetings to create a community among mentees while providing communication and support.}
      \resumeItemListEnd
\resumeSubHeadingListEnd

%-----------SKILLS-----------
\section{Skills}
\begin{tightItemize}
    \item Behavioral Management
    \item Counseling and Mentoring
    \item Program Coordination and Workshop Facilitation
    \item Research and Data Analysis
\end{tightItemize}



%-------------------------------------------
\end{document}
